Union and Intersection Contracts Are Hard, Actually

### 2021-09-16 paper.tex
Final overfull hboxes

Castagna and Lanvin~\cite{CastagnaLanvinGradualUnionIntersection} introduce a
gradual type system based on so-called set-theoretic
types~\cite{SetTheoreticTypes}.  Set-theoretic types feature unions,
intersections, negation types together with a notion of subtyping. This work
adheres to the \emph{static first school} (see~\cite{practiceTheoryGrad}) of
gradual typing: the reason for gradual types is to allow for a less precise type
information. It follows that their goals and constraints are somehow different,
resulting in the absence of first-class contracts. As for any gradual type
system, they do have to implement casts~---~that are very close to
contracts~---~for unions and intersections, but these casts are neither visible
nor available to the programmer. Obviously, no contracts mean no user-defined
contracts as well.

@@

Designing a language with union and intersection contracts means
making difficult choices: some features of union and intersection
contracts and of the rest of the language must be abandoned. Various
trade-offs can be made, but it is worth mentioning that implementing a
system with union and intersection contracts appears to be pretty
complex a task when unions and intersections are fairly complete.

>>>>

Castagna and Lanvin~\cite{CastagnaLanvinGradualUnionIntersection} introduce a
gradual type system based on set-theoretic
types~\cite{SetTheoreticTypes}.  Set-theoretic types feature unions,
intersections, negation types together with a notion of subtyping. This work
adheres to the \emph{static first school} (see~\cite{practiceTheoryGrad}) of
gradual typing: the reason for gradual types is to allow for a less precise type
information. It follows that their goals and constraints are somehow different,
resulting in the absence of first-class contracts. As for any gradual type
system, they do have to implement casts~---~that are very close to
contracts~---~for unions and intersections, but these casts are neither visible
nor available to the programmer. Obviously, no contracts mean no user-defined
contracts as well.

@@

Designing a language with union and intersection contracts necessarily
means
making difficult choices: some features of union and intersection
contracts and of the rest of the language must be abandoned. Various
trade-offs can be made, but it is worth mentioning that implementing a
system with union and intersection contracts appears to be pretty
complex a task when unions and intersections are fairly complete.
